\Large \bf One-Step, Three-Factor Authentication with Custom-Fit, In-Ear EEG

### 2017-02-16 paper.tex
Adding FRR to captions of figures 3 and 4

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG}

@@

We find that we can achieve low false acceptance rates (FAR) and false rejection rates (FRR) with a single, 
three-electrode earpiece. Interestingly, we found that performance improves in the ear compared to a single electrode on the scalp.
Additionally, we find that a passthoughts could not be spoofed by imposters, even when the imposters had the user's earpiece and knew their chosen passthoughts.
We discuss future work to investigate the robustness of passthoughts in day-to-day life, and raise questions about how and why passthoughts work as well as they do.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=.9\linewidth]{./figures/mean-far-and-frr-by-electrode-config.png}
\caption{FAR by electrode configuration. All electrodes combined achieves a perfect score. We achieve the next best scores using data from the left ear only.}
\label{fig:meanByElectrode}
\end{figure*}

@@

In the previous section, we trained and tested a passthought classifier with each task as the passthought, for all participants. Our analyses revealed the left produced decent results. Focusing on the left ear, we filter our results for the best-performing tasks. We rank tasks by lowest FAR and, given a tie, the lowest FRR (Table \ref{tab:best}). Overall, we find  a mean FAR of zero and mean FRR of 0.017\%.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=.9\linewidth]{./figures/mean-far-and-frr-by-task.png}
\caption{FAR by task, across all subjects, using data from the left ear only.}
\label{fig:meanByTask}
\end{figure*}

>>>>

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf One-Step, Three-Factor Authentication with Custom-Fit, In-Ear EEG}

@@

We find that we can achieve low false acceptance rates (FAR) and false rejection rates (FRR) with a single, 
three-electrode earpiece. Interestingly, we found that performance improves in the ear compared to a single electrode on the scalp, a site typically used for collecting EEG data.
Additionally, we find that a passthoughts could not be spoofed by imposters, even when the imposters had the user's earpiece and knew their chosen passthoughts.
We discuss future work to investigate the robustness of passthoughts in day-to-day life, and raise questions about how and why passthoughts work as well as they do.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=.9\linewidth]{./figures/mean-far-and-frr-by-electrode-config.png}
\caption{FAR and FRR by electrode configuration. All electrodes (Fp1, right, and left ear channels) combined achieves a perfect FAR score. We achieve the next best scores using data from the left ear only.}
\label{fig:meanByElectrode}
\end{figure*}

@@

In the previous section, we trained and tested a passthoughts classifier with each task as the passthought, for all participants. Our analyses revealed the left ear alone produced decent results. Focusing on the left ear, we filter our results for the best-performing tasks. We rank tasks by lowest FAR and, given a tie, the lowest FRR (Table \ref{tab:best}). Overall, we find  a mean FAR of zero and mean FRR of 0.017\%.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=.9\linewidth]{./figures/mean-far-and-frr-by-task.png}
\caption{FAR and FRR results by task, across all subjects, using data from the left ear only.}
\label{fig:meanByTask}
\end{figure*}
